Data Story

### 2023-10-27 about.qmd
Project Update

@@

##### Is public housing in Singapore affordable for the average Singaporean?

>>>>

## Is Public Housing in Singapore Affordable for the Average Singaporean?

@@

In Singapore, housing affordability has been an increasing worry for future Singaporeans. However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD \$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012). While Mr Tharman argued the housing grants could provide support for low-income household, many Singaporeans expressed concern about the long-term viability of such claims, especially in the face of the constant rising cost of living and property prices.
